### 2019-04-05 papers/journal/synth-dia.tex
Dia is complet

	  %le <-> pm
	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$ $Q_{c7}$} (pm);
	   \path (ee) edge[bend right=32, text width=2.0cm] node [below,right=0.1] {{$R_{8}$},$Q_{a7}$, $Q_{b7}$,$R_{7}$} (le);

@@

	  %le <-> pm
	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$ $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
	  }}
	  %ee -> le
	   \path (ee) edge[bend right=32, text width=2.0cm] node [below,right=0.1] {{$R_{8}$},$Q_{a7}$, $Q_{b7}$,$R_{7}$} (le);
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);

>>>>

	  %le <-> pm
	  \path (le) edge[bend right=55] node [above] {$Q_{b7}$, $Q_{c7}$} (pm);
	  \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);

@@

	  %le <-> pm
	  	  \path (le) edge[bend right=45] node [above] {$Q_{b7}$, $Q_{c7}$,{\color{blue}{ \textbf{$R_{7}$}}}} (pm);
	%  \path (le) edge[bend right=45] node [above] {Qb7 Qc7,{\color{blue} { \textbf{R7}}}} (pm);

	  %le <-> ee
	  {\color{red} { \path (le) edge[bend right] node [below,rotate=50] {{\color{blue} { {\textbf{{$R_{8}$}}}}}{\color{black},} {\color{blue} {$Q_{a7}$}}} (ee);
	  }}
	  %ee -> le
	   \path (ee) edge[bend right=32, text width=1.8cm] node [below,right=0.1] {{$R_{8}$}, $Q_{a7}$, $Q_{b7}$, $R_{7}$} (le);
%	  \path (ee) edge[bend right] node [text width=1.5cm, below,rotate=50] {{R8}, Qa7, Qbc7,R7} (le);
